Fine-scale Twitter Big Data Reveals Neighborhood Inequalities in Mental Health Effects of High Temperatures

### 2021-04-12 doc/temp-sentiment.tex
acknowledgements

@@

\section{Acknowledgements}
For funding, advising, SESYNC grant number?, etc.
This work was supported by the National Socio-Environmental Synthesis Center (SESYNC) under funding received from the National Science Foundation DBI-1639145.

>>>>

% More nuanced interpretation: optimal temperature for poor & minority neighborhoods are much lower.

@@

\section{Acknowledgements}
This work was supported by the National Socio-Environmental Synthesis Center (SESYNC) under funding received from the National Science Foundation DBI-1639145.  Additionally, cloud resources for this project were provided for the Microsoft Azure cloud by Microsoft's AI for Earth program, grant number .
